\documentclass[9pt]{extarticle}

% packages
\usepackage[utf8]{inputenc}
\usepackage[lmargin=11em, rmargin=6em, bmargin=6em, tmargin=6em]{geometry}
\usepackage[document]{ragged2e}
\usepackage[none]{hyphenat}
\usepackage{paracol}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{titling}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{xifthen}
\usepackage{setspace}

% make colors
\definecolor{lightColor}{HTML}{9a9c9d}
\definecolor{darkColor}{HTML}{3a3c3d}

% assign colors
\colorlet{title}{darkColor}
\colorlet{section}{lightColor}
\colorlet{subsection}{darkColor}
\colorlet{bullet}{lightColor}
\colorlet{setting}{lightColor}
\colorlet{divider}{lightColor}
\colorlet{link}{darkColor}

% settings
\author{Jack Cogdill}
\setmainfont{Roboto}
\pagenumbering{gobble}
\maxdeadcycles=200
\flushbottom
\setlength\parindent{0pt}
\setlist[trivlist]{itemsep=0.1em, topsep=0pt, parsep=0pt, partopsep=0pt}

% title formatting
\titleformat{\section}
    {\color{section}\Large\bfseries}
    {}
    {0em}
    {}[\color{divider}\vskip0.5em\hrule height 0.25pt]

% renew commands
\renewcommand{\baselinestretch}{1}
\newcommand{\socialsep}{\quad{\color{lightColor}\textbar}\quad}
\renewcommand{\maketitle}{
    \begin{minipage}[t]{0.45\textwidth}
        \color{title}\fontsize{28pt}{1em}\bfseries\theauthor
    \end{minipage}%
    \begin{minipage}[t]{0.55\textwidth}
        \begin{spacing}{1.3}
            \color{lightColor} 200 Eheart St SE, Apt. 1, Blacksburg, VA 24060 \\
            \color{link}
            \href{http://jackcogdill.us/}{jackcogdill.us} \socialsep
            \href{mailto:jackcog@vt.edu}{jackcog@vt.edu} \socialsep
            (765) 314-1337
        \end{spacing}
    \end{minipage}
}

% new commands
\newcommand{\ChronoSubsection}[5]{
    \makebox(-5,5)[rt]{\footnotesize\color{setting}\textit{\shortstack[r]{#3\\#4}}}
    {\hspace{-0.25em}\large\bfseries\color{subsection}%
        #1%
        \ifthenelse{\isempty{#2}}%
            {}% Nothing
            {, #2}%
    }%
    \begin{trivlist}
        \color{bullet}
        #5
    \end{trivlist}
}
\newcommand{\Subsection}[2]{
    {\normalsize\bfseries\color{subsection}#1}
    \begin{trivlist}
        \color{bullet}
        #2
    \end{trivlist}
}
\newcommand{\ChronoItem}[2]{
    \item {\color{bullet}#1 | {\footnotesize\textit{#2}}}
}
\newcommand{\vsubspace}{\vspace{2em}}
\newcommand{\vmainspace}{\vspace{3em}}

\begin{document}
\maketitle
\columnratio{0.64,}
\setlength{\columnsep}{5em} % Separation between columns
\begin{paracol}{2}
    \begin{leftcolumn}
        \section{Experience}
            \ChronoSubsection{Software Engineer Intern}{Capital One}{Richmond, VA}{June -- Aug. 2018}{
                \item Upcoming software engineer intern
            }
            \vsubspace
            \ChronoSubsection{Software Development Intern}{Faithlife}{Bellingham, WA}{May -- Aug. 2017}{
                \item Used C\#, JavaScript, CSS to contribute new features and bug fixes
                \item Pushed all code to production for Bible study software `Logos'
                \item Worked on team of senior devs and participated in sprint meetings
                \item Created a team with a marketer, developer, intern for internal hackathon
                \item Learned about all aspects of development by getting coffee with 25+ employees from executive, marketing, design, customer service
            }
        \vmainspace
        \section{Projects}
            \ChronoSubsection{Bird Song}{HackDuke}{Duke University}{Oct. 2017}{
                \item Developed a swarm intelligence platform for classifying bird songs
                \item Used JavaScript for backend server and client code
                \item The website updates real-time using WebSockets
            }
            \vsubspace
            \ChronoSubsection{Hack Attack}{Bitcamp}{UMD \& Virginia Tech}{Apr. -- May 2017}{
                \item Used PHP, JavaScript, and CSS to develop a website
                \item 1-on-1 real-time challenges to teach basic programming
                \item Expanded for a Facebook event hosted by Hackers at VT
                \item Created a tournament-style bracket with 95+ participants who competed in the cryptography and capture the flag challenges
            }
            \vsubspace
            \ChronoSubsection{Stealth PNG}{}{Charlotte, NC}{Apr. 2014}{
                \item Used C to write a steganography program
                \item Hide files or plaintext data inside PNG images
                \item Stores the encrypted data in the least two significant bits of pixels' color components (looks unchanged to the human eye)
            }
        \vmainspace
        \section{Skills}
            \Subsection{Programming}{
                \item Python, C, Java, Git, NodeJS, Bash, LaTeX
            }
            \vsubspace
            \Subsection{Web}{
                \item CSS, Sass, JavaScript, React, HTML
            }
            \vsubspace
            \Subsection{Languages}{
                \item English
                \item Japanese, Limited Working Proficiency
            }
    \end{leftcolumn}
    \begin{rightcolumn}
        \section{Education}
            \Subsection{Virginia Tech}{
                \item Expected Graduation: Dec. 2018
                \item B.S. in Computer Science
                \item 3.73 GPA
                \item Minor in Japanese Studies
            }
        \vmainspace
        \section{Extracurricular Activity}
            \Subsection{Hackers at Virginia Tech}{
                \ChronoItem{Leadership Team}{Feb. 2017 -- Present}
            }
            \vsubspace
            \Subsection{Teaching Assistant}{
                \ChronoItem{CS 1044, CS 2114}{Aug. 2017 -- Present}
            }
            \vsubspace
            \Subsection{Computer Science Mentoring}{
                \ChronoItem{Mentor}{Jan. 2018 -- Present}
            }
            \vsubspace
            \Subsection{Kaiwa no Kai (Japanese Conversation Group)}{
                \ChronoItem{Member}{Aug. 2015 -- Present}
            }
        \vmainspace
        \section{Honors \& Awards}
            \Subsection{Computer Science Resources Consortium Scholarship}{
                \ChronoItem{Recipient}{2016 -- 2017}
            }
            \vsubspace
            \Subsection{Dean's List with Distinction}{
                \ChronoItem{Recipient}{Spring \& Fall 2017}
            }
    \end{rightcolumn}
\end{paracol}

\end{document}
